%! suppress = MissingImport
\documentclass[8pt]{developercv}

\newcommand{\linebreaksmall}{\vspace{2mm}}
\begin{document}

\begin{minipage}[t]{0.45\textwidth}
    \vspace{-\baselineskip}
    \colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Daniel}}}}}

    \colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Draper}}}}}

    \vspace{6pt}

    {\large Lead Engineer}
\end{minipage}
\begin{minipage}[t]{0.275\textwidth}
    \vspace{-\baselineskip}
    \icon{MapMarker}{9}{Karlsruhe, Germany}\\
    \icon{Phone}{9}{+49 176 95767859}\\
    \icon{At}{9}{\color{blue}{\href{mailto:germandrummer92@gmail.com}{germandrummer92@gmail.com}}}\\
\end{minipage}
\begin{minipage}[t]{0.275\textwidth}
    \vspace{-\baselineskip}
    \icon{Github}{9}{\color{blue}{\href{https://github.com/germandrummer92}{github.com/germandrummer92}}}\\
    \icon{Linkedin}{9}{\color{blue}{\href{https://www.linkedin.com/in/daniel-draper92/}{linkedin.com/in/daniel-draper92}}}\\
\end{minipage}

\vspace{0.6cm}

\cvsect{Cover Letter --- Senior Software Engineer, Add-ons (Mozilla)}
\vspace{0.3cm}

Firefox has been my primary browser for over ten years --- for work, personal browsing, and everything in between.
I rely on add-ons daily, and the ecosystem they enable is one of the things that makes Firefox irreplaceable to me.
More broadly, I care deeply about the open web.
The idea that a single company's browser engine should define how the internet works is something I actively push back on, and Mozilla is the most credible organization fighting that fight.
That is why this role excites me: the chance to work on the platform that keeps the Firefox add-ons ecosystem healthy, trustworthy, and open.

\linebreaksmall

\textbf{Why I am a strong fit.}
I bring 9+ years of full-stack experience building web platforms at scale.
At octomind I built the product from MVP through a \$4.8M seed round, shipping 20+ deployments per day with a change failure rate under 5\%.
At understand.ai I scaled an annotation platform to thousands of concurrent users and 100M+ annotations.
Both roles demanded exactly what AMO needs: performant React/TypeScript frontends, robust backends, strong testing discipline, and the ability to keep a platform reliable under real user load.

\linebreaksmall

\textbf{On Django and learning new stacks.}
While I have not used Django professionally, my career is a track record of ramping up fast on new technologies and delivering quickly.
At LogMeIn, I was selected as the only German engineer for an international team that shipped a cross-platform RTC app from zero to production in under four months --- in a stack I had not used before.
I have deep Python experience from my ML work and genuinely enjoy learning the intricacies of new frameworks.
Django will not be a bottleneck.

\linebreaksmall

\textbf{Open source.}
I have contributed to several open-source projects: a feature contribution to Apache Libcloud, a bugfix to Jest, a feature for Pylint, and bugfixes for Streamlink.
These are modest individually, but they reflect a habit: when I use a tool and find something broken or missing, I fix it upstream rather than working around it.
I would welcome the chance to work in the open full-time.

\linebreaksmall

\textbf{Accessibility and security.}
As lead engineer at octomind, I owned both.
We maintained a fully responsive frontend throughout the product's life --- sometimes by deliberately scoping features to where they made sense rather than forcing a subpar mobile experience.
On security, we operated for three years without a single critical vulnerability, a record I take seriously given that our product ran customer code in CI pipelines.

\linebreaksmall

\textbf{On the Senior IC role.}
I am drawn to indirect leadership: raising the bar through code quality, testing culture, and mentorship rather than through a title.
At octomind I built that culture from scratch --- TDD, peer review, ADRs, on-call practices --- and I would bring the same instinct to AMO.
Even in a Senior Engineer role, I will naturally look for opportunities to drive technical standards and help the team ship with confidence.

\vspace{0.3cm}

I would love to discuss how my experience can contribute to the Add-ons team. Thank you for considering my application.

\end{document}
