%! suppress = MissingImport
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[8pt]{developercv} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------
\ifdefined\generated
\else
\newcommand{\generated}{manually}
\fi

\newcommand{\linebreaksmall}{\vspace{2mm}}
\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

    \begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
        \vspace{-\baselineskip} % Required for vertically aligning minipages
        % If your name is very short, use just one of the lines below
        % If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
        \colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Daniel}}}}} % First name

        \colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Draper}}}}} % Last name

        \vspace{6pt}

        {\large Lead Engineer} % Career or current job title
    \end{minipage}
    \begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the first row of icons
        \vspace{-\baselineskip} % Required for vertically aligning minipages

        % The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
        % Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
        \icon{MapMarker}{9}{Karlsruhe, Germany}\\
        \icon{Phone}{9}{+49 176 95767859}\\
        \icon{At}{9}{\color{blue}{\href{mailto:germandrummer92@gmail.com}{germandrummer92@gmail.com}}}\\
    \end{minipage}
    \begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the second row of icons
        \vspace{-\baselineskip} % Required for vertically aligning minipages

        % The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
        % Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
        \icon{Github}{9}{\color{blue}{\href{https://github.com/germandrummer92}{github.com/germandrummer92}}}\\
        \icon{Linkedin}{9}{\color{blue}{\href{https://www.linkedin.com/in/daniel-draper92/}{linkedin.com/in/daniel-draper92}}}\\
    \end{minipage}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------
    \cvsect{Summary}
    \vspace{0.5cm}

    \begin{minipage}[t]{0.45\textwidth}
        \vspace{-\baselineskip}

        Versatile full-stack AI/ML engineer turned technical leader with 9+ years across \textbf{AI platforms}, \textbf{distributed systems}, and \textbf{cloud-native SaaS}.
        I lead by example: writing code test-first, reviewing rigorously, raising the bar on quality, and the teams I build follow.
        One engineer told me I ``made them care again'' about software craftsmanship.
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.5\textwidth}
        \vspace{-\baselineskip}
        \begin{itemize}[leftmargin=*, noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
            \item \textbf{Full Stack:} TypeScript/Node.js, Python, React/Next.js, Vue.js, Swift, Go, Java
            \item \textbf{Infrastructure:} Kubernetes, AWS/GCP, Docker, Postgres, MongoDB
            \item \textbf{AI/ML:} TensorFlow/Keras, Agentic AI, Computer Vision, Data Pipelines
            \item \textbf{Engineering:} TDD, System Design, ADRs, CI/CD, Code Review Culture
            \item \textbf{Product \& Leadership:} Continuous Discovery (Product Trio), Hiring, Technical Strategy, Mentorship
        \end{itemize}
    \end{minipage}

    \vspace{0.4cm}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

    \cvsect{Experience}

    \begin{entrylist}
        \entry
        {2023 -- Current}
        {Lead/Founding Engineer}
        {octomind gmbH}
        {\vspace{-\baselineskip}\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
            \item Architected CI/CD and engineering standards that enabled 20+ deployments/day with CFR <5\% while scaling from MVP to \$4.8M seed round.
            \item Grew the engineering team from 1 to 8, owning all hiring and establishing a culture of TDD, peer review, and ADRs for architectural decisions.
            \item Actively leading development across the full stack, including agentic AI and cloud infrastructure.
            \item Established on-call procedures and production reliability practices. Built an internal agentic benchmark running on every PR to catch AI regressions early.
            \item Part of the Product Trio (Continuous Discovery), co-defining product opportunities alongside PM and UX.
        \end{itemize}
        \texttt{TypeScript}\slashsep\texttt{Node.js}\slashsep\texttt{Next.js/React}\slashsep\texttt{Postgres}\slashsep\texttt{Kubernetes}\slashsep\texttt{Agentic AI}} \linebreaksmall
        \entry
        {2019 -- 2023}
        {Senior Full-Stack ML Engineer}
        {understand.ai gmbH}
        {\vspace{-\baselineskip}\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
            \item Built and scaled an annotation platform for autonomous driving, serving 500+ concurrent annotators and producing 100M+ annotations across TB-scale 2D/3D datasets.
            \item Led a cross-functional org-wide initiative to optimize data pipeline DevEx, reducing import/export latency by >50\%.
            \item Engineered high-performance frontends (Vue.js/OpenGL), scalable MongoDB backends, and CV models (TensorFlow/Keras).
            \item Involved in 10+ engineering hires. Founded the UAI Engineering Day --- internal tech conference (30--40 attendees, external speakers), also used as a recruiting event.
        \end{itemize}
        \texttt{Python}\slashsep\texttt{TypeScript}\slashsep\texttt{Vue.js}\slashsep\texttt{Node.js}\slashsep\texttt{MongoDB}\slashsep\texttt{Kubernetes}\slashsep\texttt{Tensorflow/Keras}} \linebreaksmall
        \entry
        {2017 -- 2019}
        {Full-Stack Mobile Applications Engineer}
        {LogMeIn Inc.}
        {Worked on the \textit{GoToMeeting} platform (80M+ meetings/year, 1M+ users). Selected as only German engineer for the international core team that shipped \textit{GoToConnect}, a full RTC-enabled cross-platform mobile app, from zero to production in under 4 months. Co-led a complete rewrite of the iOS \textit{GoToMeeting Messenger} app, achieving feature parity with Android in 6 months with zero critical bugs.
        \linebreaksmall \\ \texttt{Swift}\slashsep\texttt{Kotlin}\slashsep\texttt{TypeScript}\slashsep\texttt{React Native}\slashsep\texttt{iOS}\slashsep\texttt{Android}} \linebreaksmall
        \entry
        {2015 -- 2017\\\footnotesize{part-time}}
        {Working Student Software Engineering}
        {1\&1 Telecommunications SE}
        {Built network/data center monitoring tools for early incident alerting across 1\&1's own data centers. SNMP querying and aggregation for datacenter-network devices.
        \linebreaksmall \\ \texttt{Java}\slashsep\texttt{Python}\slashsep\texttt{Ansible}\slashsep\texttt{Docker}}
    \end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

    \cvsect{Education}

    \begin{entrylist}
        \entry
        {2015 -- 2017}
        {Computer Science, MSc -- Focus: ML/AI, NLP, Speech Recognition}
        {Karlsruhe Institute of Technology}
        {Thesis: \color{blue}{\href{https://github.com/Germandrummer92/master-thesis}{Available on GitHub}}.}
        \entry
        {2012 -- 2015}
        {Computer Science, BSc}
        {Karlsruhe Institute of Technology}
        {Thesis: \color{blue}{\href{https://github.com/Germandrummer92/Bachelor-Thesis}{Available on GitHub}}.}
    \end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

    \begin{minipage}[t]{0.3\textwidth}
        \vspace{-\baselineskip} % Required for vertically aligning minipages

        \cvsect{Languages}
        \newline
        \textbf{German} - native\\
        \textbf{English} - near native\\


    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.3\textwidth}
        \vspace{-\baselineskip} % Required for vertically aligning minipages

        \cvsect{Outside of Work}

        Playing percussion/timpani in 3+ symphonic orchestras.
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.3\textwidth}
        \vspace{-\baselineskip} % Required for vertically aligning minipages

        \cvsect{Non-profit}

        2017 - Orangutan Foundation International - Construction Volunteer in Pangkalan Bun, Indonesia.
    \end{minipage}
    \mbox{}
    \vfill
    \begin{minipage}[t]{1.0\textwidth}
        \centering{\footnotesize{This document was generated \generated~on \today. Source Code available on \color{blue}{\href{https://github.com/Germandrummer92/resume}{GitHub}}.}}

    \end{minipage}

%----------------------------------------------------------------------------------------

\end{document}
